---
title: "Capstone_MASTER_DataViz"
author: "Thea B."
date: "4/3/2021"
output: html_document
---

#Loading data and packages
```{r}
LTM_cols <- read.csv("LTM_cols_April3.csv", 
                     stringsAsFactors = TRUE)
library(pacman)
p_load(cowplot, tidyverse, haven, summarytools, survey, srvyr, plotrix, jtools, tableone, lmtest, Hmisc, dummies, aod, RColorBrewer, viridis)

?read.csv
```

#Reordering variables
```{r}
#Preg Provider
LTM_cols$preg_provider_4 <- factor(LTM_cols$preg_provider_3,
                    levels = c("OB or OBGYN", "Family Medicine Doctor", "Doctor Unsure Type", "CNM", "NP or PA")) 
#Race
LTM_cols$racegrp_4 <- factor(LTM_cols$racegrp_3,
                    levels = c("White (non-Hispanic)", "Black (non-Hispanic)", "Hispanic/Latina", "Asian/Pacific Islander (non-Hispanic)", "Other/Mixed Race (non-Hispanic)"))
##Checking
LTM_cols %>%
  group_by(racegrp_4) %>%
  count() #ok!
#Education
LTM_cols$education_4 <- factor(LTM_cols$education_3,
                    levels = c("Less than High School", "High School Diploma or GED", "College Degree", "Graduate Degree"))
#Primary language
LTM_cols$prim_lang_4 <- factor(LTM_cols$prim_lang_3,
                    levels = c("English", "Spanish", "Other"))

#new version of race variable for better legend
LTM_cols$racegrp_leg <- NA
LTM_cols$racegrp_leg[LTM_cols$racegrp == 1] = 1
LTM_cols$racegrp_leg[LTM_cols$racegrp == 2] = 2
LTM_cols$racegrp_leg[LTM_cols$racegrp == 3] = 3
LTM_cols$racegrp_leg[LTM_cols$racegrp == 4] = 4
LTM_cols$racegrp_leg[LTM_cols$racegrp == 5 | LTM_cols$racegrp == 6 | LTM_cols$racegrp == 7] = 5
LTM_cols$racegrp_leg <- factor(LTM_cols$racegrp_leg, levels = c(1,2,3,4,5),
                        labels = c("Hispanic/Latina", "White", "Black", "Asian/Pacific Islander", "Other/Mixed Race"))

LTM_cols$racegrp_leg_ordered <- factor(LTM_cols$racegrp_leg,
                                       levels = c("White", "Black", "Hispanic/Latina", "Asian/Pacific Islander", "Other/Mixed Race"))
```

#Subsetting to match excl criteria
##Full study population
```{r}
names(LTM_cols)
LTM_SA_A <- subset(LTM_cols, !is.na(preg_provider_4))
names(LTM_SA_A) 
LTM_SA_A %>% 
  group_by(ppvisit_SA) %>%
  count()
ctable(LTM_SA_A$ppvisit_SA, LTM_SA_A$Q1415c)
LTM_SA_B <- subset(LTM_SA_A, (ppvisit_SA == "1 or more" & !is.na(Q1415c)) | ppvisit_SA == "0") 
LTM_SA_B %>%
  group_by(ppvisit_SA) %>%
  count()
```
##Subsetting data to match excl criteria - main study sample
```{r}
LTM_cols_3 <- subset(LTM_cols, !is.na(postpartum_visit))
LTM_cols_3 %>%
  group_by(postpartum_visit) %>%
  count()
#Postpartum visits at least one:
LTM_cols_4 <- subset(LTM_cols_3, postpartum_visit >= 1)
LTM_cols_4 %>%
  group_by(postpartum_visit) %>%
  count()
#Complete data on provider type:
LTM_cols_5 <- subset(LTM_cols_4, !is.na(preg_provider_4))
LTM_cols_5 %>%
  group_by(preg_provider_4) %>%
  count()
#Complete data on depression screening:
LTM_cols_6 <- subset(LTM_cols_5, !is.na(depression_screening))
LTM_cols_6 %>%
  group_by(preg_provider_4) %>%
  count()
```
##Subsetting data to match excl criteria - sub-sample
```{r}
LTM_mini_SA <- subset(LTM_SA_B, ppvisit_SA == "0")
LTM_mini_SA %>%
  group_by(ppvisit_SA) %>%
  count()
```

#Data Visualization
#Univariate
##Main
```{r}
#provider type bargraph
prov_type_main_bar <- LTM_cols_6 %>%
  filter(!is.na(preg_provider_4)) %>%
ggplot(aes(x = preg_provider_4)) +
  geom_bar(color = "indianred3",
           fill = "indianred3") +
  labs(title = "Distribution of Maternity Care Provider Type, Main Study Sample",
       x = "Maternity Care Provider Type",
       y = "Count") +
  scale_y_continuous(breaks = seq(0, 2000, 250)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#PPD screening bargraph
PPD_screening_main_bar <- LTM_cols_6 %>%
  filter(!is.na(depression_screening)) %>%
ggplot(aes(x =depression_screening)) +
  geom_bar(color = "indianred3",
           fill = "indianred3") +
  labs(title = "Distribution of PPD Screening, Main Study Sample",
       x = "PPD Screening",
       y = "Count")
```
##Sub
```{r}
#Mental health concern during pregnancy bargraph
MH_concern_bar_main <- LTM_cols_6 %>%
  filter(!is.na(preg_MH_issue)) %>%
ggplot(aes(x = preg_MH_issue)) +
  geom_bar(color = "indianred3",
           fill = "indianred3") +
    xlab("Depression or Anxiety During Pregnancy") +
    ylab("Count") +
    ggtitle("Distribution of Depression or Anxiety During Pregnancy, \nMain Study Sample")

#Mental health concern during pregnancy SUB-SAMPLE bargraph
MH_concern_bar_sub <- LTM_mini_SA %>%
  filter(!is.na(preg_MH_issue)) %>%
ggplot(aes(x = preg_MH_issue)) +
  geom_bar(color = "indianred3",
           fill = "indianred3") +
    xlab("Depression or Anxiety During Pregnancy") +
    ylab("Count") +
    ggtitle("Distribution of Depression or Anxiety During Pregnancy, \nStudy Sub-Sample")

#plotting side by side
MH_concern_bar_main_sub <- plot_grid(MH_concern_bar_main, MH_concern_bar_sub)
```
###Exporting
```{r, eval = FALSE}
ggsave("Provider_Type_Bar_Main.png", plot = prov_type_main_bar, width = 15, height = 15, units = "cm")

ggsave("PPD_Screening_Bar_Main.png", plot = PPD_screening_main_bar, width = 15, height = 15, units = "cm")

ggsave("Preg_MH_concern_main_bar.png", plot = MH_concern_bar_main, width = 15, height = 15, units = "cm")

ggsave("Preg_MH_concern_sub_bar.png", plot = MH_concern_bar_sub, width = 15, height = 15, units = "cm")
```

#Bivariate - stratified by Prov Type
```{r}
##making color palette
mycols2 <- plasma(5, begin = 0.25, end = 0.82, direction = -1)

#race
race_by_prov_bar <- LTM_cols_6 %>%
  filter(!is.na(preg_provider_4)) %>%
  filter(!is.na(racegrp_4)) %>%
  ggplot(aes(x = preg_provider_4, fill = racegrp_leg_ordered)) +
  geom_bar(position = "fill") +
  labs(title = "Race by Provider Type",
       fill = "Race",
       x = "Maternity Care Provider Type",
       y = "Proportion") +
  scale_y_continuous(breaks = seq(0.00, 1.00, 0.10)) +
  scale_fill_manual(values = mycols2) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1)) +
  theme(text = element_text(size=15)) +
  guides(fill=guide_legend(title=NULL)) +
  theme(legend.text = element_text(size = 12)) +
  theme(legend.position="top")
  

#insurance
##making color palette
mycols_ins <- plasma(2, begin = 0.25, end = 0.5, direction = -1)

insurance_prov_bar <- LTM_cols_6 %>%
  filter(!is.na(preg_provider_4)) %>%
  filter(!is.na(insurance_4)) %>%
  ggplot(aes(x = preg_provider_4, fill = insurance_4)) +
  geom_bar(position = "fill") +
  labs(title = "Insurance Coverage by Provider Type",
       fill = "Insurance Coverage",
       x = "Maternity Care Provider Type",
       y = "Proportion") +
  scale_y_continuous(breaks = seq(0.00, 1.00, 0.10)) +
  scale_fill_manual(values = mycols_ins) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1)) +
  theme(text = element_text(size=15)) +
  guides(fill=guide_legend(title=NULL)) +
  theme(legend.position="top")

##education
education_prov_bar <- LTM_cols_6 %>%
  filter(!is.na(preg_provider_4)) %>%
  filter(!is.na(education_4)) %>%
  ggplot(aes(x = preg_provider_4, fill = education_4)) +
  geom_bar(position = "fill") +
  labs(title = "Education by Provider Type",
       fill = "Highest Level Education",
       x = "Maternity Care Provider Type",
       y = "Proportion") +
  scale_y_continuous(breaks = seq(0.00, 1.00, 0.10)) +
  scale_fill_manual(values = mycols2) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))

#Primary language
primlang_prov_bar <- LTM_cols_6 %>%
  filter(!is.na(preg_provider_4)) %>%
  filter(!is.na(prim_lang_4)) %>%
  ggplot(aes(x = preg_provider_4, fill = prim_lang_4)) +
  geom_bar(position = "fill") +
  labs(title = "Primary Language by Provider Type",
       fill = "Primary Language Spoken at Home",
       x = "Maternity Care Provider Type",
       y = "Proportion") +
  scale_y_continuous(breaks = seq(0.00, 1.00, 0.10)) +
  scale_fill_manual(values = mycols2) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
```
##Exporting
```{r, eval = FALSE}
#race
ggsave("Race_by_Prov_bar.png", plot = race_by_prov_bar, width = 20, height = 18, units = "cm")

#insurance
ggsave("Insurance_by_Prov_bar.png", plot = insurance_prov_bar, width = 14, height = 15, units = "cm")

#education
ggsave("Education_by_Prov_bar.png", plot = education_prov_bar, width = 20, height = 15, units = "cm")

#prim lang
ggsave("PrimLang_by_Prov_bar.png", plot = primlang_prov_bar, width = 20, height = 15, units = "cm")
```
#Bivariate - stratified by PPD Screening
```{r}
#education
mycols_screening <- plasma(2, begin = 0.6, end = 0.8, direction = -1)
##position fill - better
screening_by_education_bar <- LTM_cols_6 %>%
  filter(!is.na(depression_screening)) %>%
  filter(!is.na(education_4)) %>%
  ggplot(aes(x = education_4, fill = depression_screening)) +
  geom_bar(position = "fill") +
  labs(title = "PPD Screening by Education",
       fill = "PPD Screening",
       x = "Highest Level of Education",
       y = "Proportion") +
  scale_y_continuous(breaks = seq(0.00, 1.00, 0.10)) +
  scale_fill_manual(values = mycols_screening) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1)) +
  theme(text = element_text(size=15)) +
  guides(fill=guide_legend(title=NULL)) +
  theme(legend.position="top")

##position dodge
LTM_cols_6 %>%
  filter(!is.na(depression_screening)) %>%
  filter(!is.na(education_4)) %>%
  ggplot(aes(x = education_4, fill = depression_screening)) +
  geom_bar(position = position_dodge(preserve = "single")) +
  labs(title = "PPD Screening by Education",
       fill = "PPD Screening",
       x = "Highest Level of Education",
       y = "Proportion") +
  scale_fill_manual(values = mycols_screening) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))

#insurance
mycols_ins_2 <- plasma(1, begin = 0.2, end = 0.3)
#position dodge - better
screening_by_ins_posdodge_bar <- LTM_cols_6 %>%
  filter(!is.na(depression_screening)) %>%
  filter(depression_screening == "Yes") %>%
  filter(!is.na(insurance_4)) %>%
  ggplot(aes(x =insurance_4, fill = depression_screening)) +
  geom_bar(position = position_dodge(preserve = "single")) +
  labs(title = "PPD Screening by Insurance Coverage",
       fill = "PPD Screening",
       x = "Insurance Coverage") +
  scale_fill_manual(values = mycols_ins_2) +
  theme(text = element_text(size=15)) +
  guides(fill=guide_legend(title=NULL)) +
  theme(legend.position="top") +  
  theme(legend.position = "none")
  

#position single
insurance_PPDscreening_bar <- LTM_cols_6 %>%
  filter(!is.na(insurance_4)) %>%
  filter(!is.na(depression_screening)) %>%
  ggplot(aes(x = insurance_4, fill = depression_screening)) +
  geom_bar(position = "fill") +
  labs(title = "PPD Screening by Insurance Coverage",
       fill = "PPD Screening",
       x = "Insurance Coverage",
       y = "Proportion") +
  scale_y_continuous(breaks = seq(0.00, 1.00, 0.10)) +
  scale_fill_manual(values = mycols_ins) +
  theme(text = element_text(size=15)) +
  guides(fill=guide_legend(title=NULL)) +
  theme(legend.position="top") 

#Primary language
mycols_num_children <- plasma(3, begin = 0.3, end = 0.7, direction = -1)

##position fill - better
screening_primlang_bar <- LTM_cols_6 %>%
  filter(!is.na(prim_lang_4)) %>%
  filter(!is.na(depression_screening)) %>%
  ggplot(aes(x = prim_lang_4, fill = depression_screening)) +
  geom_bar(position = "fill") +
  labs(title = "PPD Screening by Primary Language",
       fill = "PPD Screening",
       x = "Primary Language",
       y = "Proportion") +
  scale_y_continuous(breaks = seq(0.00, 1.00, 0.10)) +
  scale_fill_manual(values = mycols_num_children) 

##position dodge
LTM_cols_6 %>%
  filter(!is.na(prim_lang_4)) %>%
  filter(!is.na(depression_screening)) %>%
  ggplot(aes(x = prim_lang_4, fill = depression_screening)) +
  geom_bar(position = position_dodge(preserve = "single")) +
  labs(title = "PPD Screening by Primary Language",
       fill = "PPD Screening",
       x = "Primary Language",
       y = "Proportion") +
  scale_y_continuous(breaks = seq(0.00, 1.00, 0.10)) +
  scale_fill_manual(values = mycols_num_children)

#Number of children - don't use
##position fill
screening_by_numchildren_bar <- LTM_cols_6 %>%
  filter(!is.na(num_children_cat_3)) %>%
  filter(!is.na(depression_screening)) %>%
  ggplot(aes(x = num_children_cat_3, fill = depression_screening)) +
  geom_bar(position = "fill") +
  labs(title = "PPD Screening by Number of Children",
       fill = "PPD Screening",
       x = "Number of Children",
       y = "Proportion") +
  scale_y_continuous(breaks = seq(0.00, 1.00, 0.10)) +
  scale_fill_manual(values = mycols_num_children)

##position dodge single
LTM_cols_6 %>%
  filter(!is.na(num_children_cat_3)) %>%
  filter(!is.na(depression_screening)) %>%
  ggplot(aes(x = num_children_cat_3, fill = depression_screening)) +
  geom_bar(position = position_dodge(preserve = "single")) +
  labs(title = "PPD Screening by Number of Children",
       fill = "PPD Screening",
       x = "Number of Children",
       y = "Proportion") +
  scale_y_continuous(breaks = seq(0.00, 1.00, 0.10)) +
  scale_fill_manual(values = mycols_num_children)
```
##Exporting
```{r, eval = FALSE}
#education
ggsave("Screening_by_Education.png", plot = screening_by_education_bar, width = 20, height = 18, units = "cm")

#insurance
ggsave("Screening_by_Ins_4Col.png", plot = insurance_PPDscreening_bar, width = 16, height = 18, units = "cm")
ggsave("Screening_by_Ins_2Col.png", plot = screening_by_education_bar, width = 20, height = 15, units = "cm")
ggsave("Screening_by_Ins_PosDodge.png", plot = screening_by_ins_posdodge_bar, width = 20, height = 18, units = "cm")

#primary language
ggsave("Screening_by_PrimLang.png", plot = screening_primlang_bar, width = 20, height = 15, units = "cm")
```
