---
title: "Capstone_Data_MASTERFile"
author: "Thea B."
date: "2/18/2021"
output: html_document
---

Cleaning & exporting cleaned dataset

#Importing original dataset
```{r}
library(pacman)
p_load(cowplot, tidyverse, haven, summarytools, survey, srvyr, plotrix, jtools, tableone, lmtest, Hmisc, dummies, aod)
LTM_sav <- read_sav("LTMdata_2.public.sav")
```
##Converting .sav to .csv and exporting
```{r, eval = FALSE}
write.csv(LTM_sav, "LTM_m.csv")
```
##Loading .csv data
```{r}
LTM <- read.csv("LTM_m.csv",
                stringsAsFactors = T)
names(LTM)
```

#Getting average number of months since birth
```{r}
mean(LTM$babyageM)
#average months = 5.68
```

#Cleaning/creating variables
##Pregnancy care provider
```{r}
LTM$preg_provider <- LTM$Q805

LTM$preg_provider_3 <- NA
LTM$preg_provider_3[LTM$preg_provider == 1] = 1
LTM$preg_provider_3[LTM$preg_provider == 2] = 2
LTM$preg_provider_3[LTM$preg_provider == 3] = 3
LTM$preg_provider_3[LTM$preg_provider == 4] = 4
LTM$preg_provider_3[LTM$preg_provider == 5 | LTM$preg_provider == 6] = 5

#Leveling and labeling
LTM$preg_provider_3 <- factor(LTM$preg_provider_3, levels = c(1, 2, 3, 4, 5), 
                    labels = c("OB or OBGYN", "Family Medicine Doctor", "Doctor Unsure Type", "CNM", "NP or PA"))
#Checking
LTM %>%
  group_by(preg_provider_3 ) %>%
  count()
```
##Depression screening
```{r}
LTM$depression_screening <- LTM$Q1415c

#Leveling and labeling
LTM$depression_screening <- factor(LTM$depression_screening, levels = c(1,2),
                                   labels = c("Yes", "No"))
#Checking
LTM %>%
  group_by(depression_screening) %>%
  count()
```
##Doula support
```{r}
LTM$doula <- LTM$Q1105

LTM$doula_3 <- NA
LTM$doula_3[LTM$doula == 1] = 1
LTM$doula_3[LTM$doula == 2 | LTM$doula == 3] = 0
LTM$doula_3 <- factor(LTM$doula_3, levels = c(1,0),
                                   labels = c("Yes", "No"))
LTM %>%
  group_by(doula_3) %>%
  count()
```
##Race
```{r}
LTM$racegrp_3 <- NA
LTM$racegrp_3[LTM$racegrp == 1] = 1
LTM$racegrp_3[LTM$racegrp == 2] = 2
LTM$racegrp_3[LTM$racegrp == 3] = 3
LTM$racegrp_3[LTM$racegrp == 4] = 4
LTM$racegrp_3[LTM$racegrp == 5 | LTM$racegrp == 6 | LTM$racegrp == 7] = 5
LTM$racegrp_3 <- factor(LTM$racegrp_3, levels = c(1,2,3,4,5),
                        labels = c("Hispanic/Latina", "White (non-Hispanic)", "Black (non-Hispanic)", "Asian/Pacific Islander (non-Hispanic)", "Other/Mixed Race (non-Hispanic)"))
LTM %>%
  group_by(racegrp_3) %>%
  count()
```
##Insurance_3
```{r}
LTM$insurance_3 <- NA
LTM$insurance_3[LTM$insurance == 1] = 1
LTM$insurance_3[LTM$insurance == 2 | LTM$insurance == 3] = 2
LTM$insurance_3[LTM$insurance == 4] = NA
LTM$insurance_3[LTM$insurance == 5] = 3
LTM$insurance_3 <- factor(LTM$insurance_3, levels = c(1,2,3),
                        labels = c("Medi-Cal", "Private", "Uninsured"))
LTM %>%
  group_by(insurance_3) %>%
  count()
```
##Insurance_4
```{r}
LTM$insurance
LTM$insurance_4 <- NA
LTM$insurance_4[LTM$insurance == 1 | LTM$insurance == 5] = 1
LTM$insurance_4[LTM$insurance == 2 | LTM$insurance == 3] = 2
LTM$insurance_4[LTM$insurance == 4] = NA
LTM$insurance_4 <- factor(LTM$insurance_4, levels = c(1,2),
                        labels = c("Medi-Cal or Uninsured", "Private"))
LTM %>%
  group_by(insurance_4) %>%
  count()
```
##Insurance_5
```{r}
LTM$insurance_5 <- NA
LTM$insurance_5[LTM$insurance == 2 | LTM$insurance == 3] = 1
LTM$insurance_5[LTM$insurance == 1 | LTM$insurance == 4 | LTM$insurance == 5] = 2
LTM$insurance_5 <- factor(LTM$insurance_5, levels = c(1,2),
                               labels = c("Private Insurance = Yes", "Private Insurance = No"))
LTM %>%
  group_by(insurance_5) %>%
  count()
```
##Insurance_6
```{r}
LTM$insurance_6 <- NA
LTM$insurance_6[LTM$insurance == 2 | LTM$insurance == 3] = 1
LTM$insurance_6[LTM$insurance == 1 | LTM$insurance == 5] = 2
LTM$insurance_6[LTM$insurance == 4] = 3
LTM$insurance_6 <- factor(LTM$insurance_6, levels = c(1,2,3),
                               labels = c("Private Insurance = Yes", "Private Insurance = No", "Private Insurance = Unsure"))
LTM %>%
  group_by(insurance_6) %>%
  count()
```
##Education level
```{r}
LTM$education <- LTM$Q1860

LTM$education_3 <- NA
LTM$education_3[LTM$education == 1 | LTM$education == 2] = 1
LTM$education_3[LTM$education == 3 | LTM$education == 4 | LTM$education == 5] = 2
LTM$education_3[LTM$education == 6 | LTM$education == 7] = 3
LTM$education_3[LTM$education == 8] = 4

LTM$education_3 <- factor(LTM$education_3, levels = c(1,2,3,4),
                          labels = c("Less than High School", "High School Diploma or GED", "College Degree", "Graduate Degree"))

LTM %>%
  group_by(education_3) %>%
  count()
```
##Number of children as categorical
```{r}
LTM$num_children <- LTM$Q610

LTM$num_children_cat_3 <- cut(LTM$num_children,
                             breaks = c(0,1,2,10),
                             labels = c("1", "2", "3 or more"),
                             include.lowest = TRUE,
                             right = TRUE)
#Checking
LTM %>%
  group_by(num_children_cat_3) %>%
  count()
```
##Primary language
```{r}
LTM$prim_lang <- LTM$Q1845

LTM$prim_lang_3 <- NA
LTM$prim_lang_3[LTM$prim_lang == 1 | LTM$prim_lang == 3] = 1
LTM$prim_lang_3[LTM$prim_lang == 2] = 2
LTM$prim_lang_3[LTM$prim_lang == 4 | LTM$prim_lang == 5] = 3

LTM$prim_lang_3 <- factor(LTM$prim_lang_3, levels = c(1:3),
                        labels = c("English", "Spanish", "Other"))

LTM %>%
  group_by(prim_lang_3) %>%
  count()
```
##Marital status v1 (4 cat)
```{r}
LTM$marital_status <- LTM$Q1820

LTM$marital_status_3 <- factor(LTM$marital_status, levels = c(1:4),
                             labels = c("Married", "Living with someone as if married", "Separated, divorced or widowed", "Single, never married"))
LTM %>% 
  group_by(marital_status_3) %>%
  count()
```
###Marital status FINAL VERSION (2 cat)
```{r}
LTM$marital_status_4 <- NA
LTM$marital_status_4[LTM$Q1820 == 1| LTM$Q1820 ==2] = 0
LTM$marital_status_4[LTM$Q1820 == 3 | LTM$Q1820 == 4] = 1
LTM$marital_status_4 <- factor (LTM$marital_status_4, levels = c(0,1), labels = c("Married or Living Together as if Married", "Single, Divorced, or Widowed"))

#Checking
LTM %>%
  group_by(LTM$marital_status_4) %>%
  count()
```
##Age (categorical)
```{r}
LTM$age_3 <- LTM$Q1842
LTM$age_cat_3 <- cut(LTM$age_3,
                             breaks = c(0,24,29,34,46),
                             labels = c("24 and under", "25-29 years", "30-34 years", "35 and over"),
                             include.lowest = TRUE,
                             right = TRUE)
LTM %>%
  group_by(age_cat_3) %>%
  count()
```
##Creating binary anxiety and depression variables
```{r}
LTM$preg_depression_3 <- NA
LTM$preg_anxiety_3 <- NA

#Anxiety:
LTM$preg_anxiety_3[LTM$Q925a >= 3
                 | LTM$Q925b >= 3] = 1
LTM$preg_anxiety_3[LTM$Q925a < 3
                 & LTM$Q925b < 3] = 0
LTM$preg_anxiety_3[is.na(LTM$Q925a)
                 |is.na(LTM$Q925b)] = NA
#Checking
LTM$preg_anxiety_3[1:100]
LTM$Q925a[1:100]
LTM$Q925b[1:100]

#Depression: 
LTM$preg_depression_3[LTM$Q925c >= 3
                 | LTM$Q925d >= 3] = 1
LTM$preg_depression_3[LTM$Q925c < 3
                 & LTM$Q925d < 3] = 0
LTM$preg_depression_3[is.na(LTM$Q925c)
                 |is.na(LTM$Q925d)] = NA
#Checking
LTM$preg_depression_3[1:100]
LTM$Q925c[1:100]
LTM$Q925d[1:100]

LTM %>%
  group_by(Q925a, Q925b, preg_anxiety_3) %>%
  count()
LTM %>%
  group_by(Q925c, Q925d, preg_depression_3) %>%
  count()
```
###Creating levels and labels for binary anxiety/depression
```{r}
#Anxiety
class(LTM$preg_anxiety_3)
class(LTM$preg_depression_3)
LTM$preg_anxiety_3 <- factor(LTM$preg_anxiety_3, levels = c(0,1),
                           labels = c("No", "Yes"))
#Checking
class(LTM$preg_anxiety_3)
levels(LTM$preg_anxiety_3)
LTM %>% 
  group_by(preg_anxiety_3) %>%
  count()

#Depression
LTM$preg_depression_3 <- factor(LTM$preg_depression_3, levels = c(0,1),
                           labels = c("No", "Yes"))
#Checking
class(LTM$preg_depression_3)
levels(LTM$preg_depression_3)
LTM %>% 
  group_by(preg_depression_3) %>%
  count()
```
##Mental health concern during pregnancy (composite of preg_anxiety and preg_depression)
```{r}
LTM$preg_MH_issue <- NA
LTM$preg_MH_issue[LTM$preg_anxiety_3 == "No" & LTM$preg_depression_3 == "No"] = 0
LTM$preg_MH_issue[LTM$preg_anxiety_3 == "Yes" | LTM$preg_depression_3 == "Yes"] = 1
LTM$preg_MH_issue <- factor(LTM$preg_MH_issue, levels = c(0,1), labels = c("No", "Yes"))
#Checking
class(LTM$preg_MH_issue)
LTM %>%
  group_by(preg_MH_issue) %>%
  count()
ctable(LTM$preg_anxiety_3, LTM$preg_depression_3)
```
##Number of postpartum visits in 8 weeks after the birth
```{r}
LTM$postpartum_visit <- LTM$Q1405

LTM$num_PP_visits_8wks <- NA
LTM$num_PP_visits_8wks[LTM$Q1405 == 0] = 0
LTM$num_PP_visits_8wks[LTM$Q1405 == 1] = 1
LTM$num_PP_visits_8wks[LTM$Q1405 == 2] = 2
LTM$num_PP_visits_8wks[LTM$Q1405 >= 3] = 3

#Leveling and labeling
LTM$num_PP_visits_8wks <- factor(LTM$num_PP_visits_8wks, levels = c(0:3), labels = c("0", "1", "2", "3 or more"))

#Checking
LTM %>%
  group_by(num_PP_visits_8wks) %>%
  count()
```
##Binary PP office visit variable for sub-analysis
```{r}
names(LTM)
class(LTM$Q1405)
LTM$ppvisit_SA <- NA
LTM$ppvisit_SA[LTM$Q1405 == 0] = 0
LTM$ppvisit_SA[LTM$Q1405 >= 1] = 1
LTM %>%
  group_by(ppvisit_SA) %>%
  count() #success!

#Labeling
LTM$ppvisit_SA <- factor(LTM$ppvisit_SA, levels = c(0,1), labels = c("0", "1 or more"))

#Checking association
ctable(LTM$preg_depression_3, LTM$ppvisit_SA)
```

#Dropping unused columns, exporting new dataset
```{r}
LTM_cols <- select(LTM, -c(mode, Q_Language, Q520, Q715, Q716, Q740, Q850, Q855, Q870, Q885, Q890, Q895, Q1110, Q1111a, Q1111b, Q1111c, Q1111d, Q1111e, Q1112, Q1113a, Q1113b, Q1113c, Q1113d, Q1113e, Q1113f, Q1113g, Q1113h, Q1113i, Q1120, Q1125, Q1130a, Q1130b, Q1130c, Q1130d, Q1130e, Q1130f, Q1132, Q1133, Q1135, Q1130a, Q1140a, Q1140b, Q1145a, Q1145b, Q1145c, Q1145d, Q1145f, Q1147a, Q1147b, Q1147c, Q1147d, Q1147e, Q1147f, Q1147g, Q1147h, Q1147i, Q1150, Q1176, Q1181, Q1185, Q1186, Q1210a, Q1210b, Q1210c, Q1210d, Q1210e, Q1210f, Q1210g, Q1210h, Q1210i, Q1210j, Q1210k, Q1210l, Q1210m, Q1210n, Q1210o, Q1215, Q1220, Q1230, Q1235, Q1240, Q1245, Q1250, Q1255, Q1260, Q1265, Q1270, Q1275a, Q1275a, Q1275b, Q1275c, Q1305, Q1310a, Q1310b, Q1310c, Q1310d, Q1315a, Q1315b, Q1315c, Q1320a, Q1320b, Q1325a, Q1325b, Q1325c, Q1415a, Q1415b, Q1480b, Q1510a, Q1510b, Q1510c, Q1525, Q1615, Q1630, Q1705a, Q1705b, Q1710a, Q1710b, Q1710c, Q1710d, Q1715a, Q1715b, Q1715c, Q1715d, Q1715e, Q1715f, Q1715g, Q1835, qdate, babyageM, Q816_TEXT, calcgestage, Q895_TEXT, Q1111_TEXT, Q1113_TEXT, Q1145_TEXT, Q1147_TEXT, Q1155, Q1165_TEXT, Q1170a, Q1170b, Q1170c, babywtgm, Q1190, Q1195, Q1255_TEXT, Q1260_TEXT, Q1515b, Q1520a, Q1520b, bfexclwks, bfwkstop, Q1620a, Q1620b, workage, Q1625a, Q1625b, workagef, Q1715_TEXT, Q1805a, Q1805b, Q1805c, height, Q1810E, Q1810S, WtBeforePreg, bmi, Q1811a, Q1811b, wtgain, Q1815a, Q1815b, currentwt, Q1825_TEXT, Q1830, Q1840))

#checking
names(LTM_cols)
```
##Exporting LTM_cols
```{r, eval = F}
write.csv(LTM_cols, "LTM_cols_M.csv", row.names = F)
```
